---
title: "Final Homework Code"
Subtitle: "Assignment Due September 20th, 2023 by 5PM"
author: "Lillian Holden"
date: "2023-09-20"
output: 
  html_document: 
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Reflection

Three things that were difficult during the homework: 
I had a hard time figuring out how to knit the the RMarkdown. I realized that I needed to put the codes into chunks, so that they were able to be run. I also had a hard time getting the codes to run because I needed to make sure the stringr library was enabled. I made sure that this was enabled by typing "library(stringr) into its own chunk. Lastly, I had a hard time getting the codes to output in the RMarkdown file, rather than the console. I solved this issue by going to the settings next to "Knit" and selecting "Chunk Output Inline." Then, I ran each chunk to display the outputs in the RMarkdown file.
 
My Peer: Allister Malik

Three things that were useful in my peers commentary: 

Two things I like about my peers code: I like that he was able to make his chunk names/category names match the title font in the HTML file. I also like that he was able to find an easier way to extract every third element in challenge 3 as I had to extract them individually. 

One thing I do not like about my peers code: One thing that I did not like about his code is that once he created a matrix of numbers in challenge 2, he did not add a code to view it in its original state before making changes to it. 


```{r}
library(stringr)
```

#Challenge 1

```{r Challenge-1}
v1 <- c("Stately,", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed.") 
str_split(v1,"Buck", n=1, simplify=FALSE)
v1[c(3,6,9,12,15,18,21)]
```
##Challenge 2

```{r Challenge-2}
m<- matrix(data=1:80, nrow=8, ncol=10, byrow=FALSE)
x<-m[,2]
x
x<-m[,c(2,3,6)]
x
x<-m[c(6,8),]
x
```
###Challenge 3

```{r}

a<-array(data=400:1, dim=c(5,5,4,4))
a
a[1,1,1,2]
a[1:5,1:5,3,3]
a[2,3,2,]
```
####Challenge 4

```{r}
Lemuroidea<-c("Cheirogaleidae", "Lepilemuridae","Indridae", "Lemuridae", "Daubentoniidae")
Lorisoidea<-c("Lorisidae","Galagidae")
Strepsirhini<-list("Lemuroidea","Lorisoidea")
Strepsirhini
Lemuroidea<-c("Cheirogaleidae", "Lepilemuridae","Indridae", "Lemuridae", "Daubentoniidae")
Lorisoidea<-c("Lorisidae","Galagidae")
Strepsirhini<-list("Lemuroidea","Lorisoidea")
names(Strepsirhini)<-list("Lemuroidea","Lorisoidea")
Strepsirhini
Lemuroidea<-c("Cheirogaleidae", "Lepilemuridae","Indridae", "Lemuridae", "Daubentoniidae")
Lorisoidea<-c("Lorisidae","Galagidae")
Strepsirhini<-list(Lemuroidea,Lorisoidea)
names(Strepsirhini)<-list("Lemuroidea","Lorisoidea")
Strepsirhini
Tarsioidea<-c("Tarsiidae")
Catarrhini<-c("Cercopithecidae","Hylobatidae","Hominidae")
Platyrrhini<-c("Cebidae","Atelidae","Pitheciidae")
Anthropoidea<-c("Platyrrhini","Catarrhini")
Haplorhini<-list(Anthropoidea,Tarsioidea)
names(Haplorhini)<-list("Anthropoidea","Tarsioidea")
Haplorhini
Haplorhini<-list(Anthropoidea,Platyrrhini,Catarrhini,Tarsioidea)
names(Haplorhini)<-list("Anthropoidea","Platyrrhini","Catarrhini","Tarsioidea")
Haplorhini
Primates<-list(Haplorhini,Strepsirhini)
names(Primates)<-list("Haplorhini","Strepsirhini")
Primates
```
#####Challenge 5 

```{r}
m3<-matrix(data=c(3,0,1,23,1,2,33,1,1,42,0,1,41,0,2),nrow=5,ncol=3,byrow=TRUE)
data.frame(m3)
df <- data.frame(m3)
df[,2] <- as.logical(df[,2])
df[,3] <- as.factor(df[,3])
str(df)
```

<center> End of Final Homework <center> 